E4-analysis-ROIs

### 2024-10-22 group-a/E1-analysis-comparison-to-Hartshorne.Rmd

```{r save validation percent in roi during validation-JH}
jh.validation.percent <- jh.validation.accuracy.data %>%
  group_by(subject_id) %>%
  slice_tail() %>%
  select(subject_id, percent_in_roi) %>%
  unnest(percent_in_roi) %>%
  group_by(subject_id) %>%
  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
  mutate(subject_id = fct_reorder(subject_id, M))

@@

jh.critical.trials.filtered.min <- jh.critical.trials %>%
  filter(!subject_id %in% jh.bad.subjects.min)

@@

#### Minimal Exclusion
As in the remote sample, we checked whether there were participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs and there were none. We then excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in `r n.jh.bad.subjects.min - length(jh.bad.subjects.prop.samples.min)` excluded participants. The following analyses included `r nlevels(droplevels(jh.critical.trials.filtered.min$subject_id))` participants.

@@

```{r group cumu fix by object-JH, message=FALSE, warning=FALSE}
jh.cumulative.fixation.windows.grouped.data.min <- jh.cumulative.fixation.windows.data.min %>%
  filter(!subject_id %in% jh.bad.subjects.min) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

@@

#correlate
jh.m3_diff_cor <- cor.test(jh.cali.analy.3$diff, jh.cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
jh.m3_diff_cor_r <- jh.m3_diff_cor$estimate
jh.m3_diff_cor_p <- jh.m3_diff_cor$p.value
```
#### Calibration
As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from `r min(jh.validation.percent$M) %>% round(digits = 2)`% to `r max(jh.validation.percent$M) %>% round(digits = 2)`%. 
Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`.

In the remote sample, we saw that calibration quality was correlated with target advantage in the pre-noun window in the restricting condition alone. This was not the case in the in-lab sample (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).

@@

```{r}
prop.samples.threshold.aggro.jh <- 0.2

@@

critical.trials.filtered.aggro.jh <- jh.critical.trials %>%
  filter(!subject_id %in% bad.subjects.aggro.jh)

n.bad.subjects.aggro.jh <- length(bad.subjects.aggro.jh)
```
#### Aggressive Exclusion
The second set of analyses used more aggressive exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.aggro.jh*100` percent of fixations or fewer landing in any ROIs. This resulted in the elimination of `r length(bad.subjects.prop.samples.aggro.jh)` participants. Second, we excluded participants with validation accuracy under `r validation.threshold.aggro.jh` percent, which eliminated an additional `r n.bad.subjects.aggro.jh - length(bad.subjects.prop.samples.aggro.jh)` participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))` participants.

@@

```{r}
cumulative.fixation.windows.grouped.data.aggro.jh <- cumulative.fixation.windows.data.aggro.jh %>%
  filter(!subject_id %in% bad.subjects.aggro.jh) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

@@

```
Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).

>>>>

```{r save validation percent in roi during validation-JH}
jh.validation.percent <- jh.validation.accuracy.data %>%
  group_by(subject_id) %>%
  #slice_tail() %>%
  select(subject_id, percent_in_roi, trial_index, phase) %>%
  unnest(percent_in_roi) %>%
  group_by(subject_id, trial_index, phase) %>%
  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
  group_by(subject_id) %>%
  mutate(calib_num = row_number()) %>%
  filter(calib_num == max(calib_num)) %>%
  select(subject_id, M, calib_num) %>%
  mutate(subject_id = fct_reorder(subject_id, M))

@@

#AJ: Cut!
# jh.critical.trials.filtered.min <- jh.critical.trials %>%
#   filter(!subject_id %in% jh.bad.subjects.min)
jh.critical.trials.filtered.min <- jh.critical.trials #The name is a lie :)

@@

```
<!--AJ: Cut
#### Minimal Exclusion
As in the remote sample, we checked whether there were participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs and there were none. We then excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in `r n.jh.bad.subjects.min - length(jh.bad.subjects.prop.samples.min)` excluded participants. The following analyses included `r nlevels(droplevels(jh.critical.trials.filtered.min$subject_id))` participants. 
-->

@@

```{r group cumu fix by object-JH, message=FALSE, warning=FALSE}
jh.cumulative.fixation.windows.grouped.data.min <- jh.cumulative.fixation.windows.data.min %>%
  #filter(!subject_id %in% jh.bad.subjects.min) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

@@

#correlate
jh.m3_diff_cor <- cor.test(jh.cali.analy.3$diff, jh.cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
jh.m3_diff_cor_r <- jh.m3_diff_cor$estimate
jh.m3_diff_cor_p <- jh.m3_diff_cor$p.value
```
```{r E1b-calib-effect, fig.cap='Calibration scores plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.'}
#I picked this one because it's the same as in E1a
ggplot(jh.cali.analy.3, aes(x=M, y=diff))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Verb Effect (ms)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

### Calibration
As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from `r min(jh.validation.percent$M) %>% round(digits = 2)`% to `r max(jh.validation.percent$M) %>% round(digits = 2)`%. 
Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`. Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.

@@

```{r}
#AJ: not actually using this
prop.samples.threshold.aggro.jh <- 0.2

@@

critical.trials.filtered.aggro.jh <- jh.critical.trials %>%
  #filter(!subject_id %in% bad.subjects.aggro.jh)
  filter(!subject_id %in% bad.subjects.validation.aggro.jh)

n.bad.subjects.aggro.jh <- length(bad.subjects.aggro.jh)
n.bad.subjects.validation.aggro.jh <- length(bad.subjects.validation.aggro.jh)
```

@@

```{r}
cumulative.fixation.windows.grouped.data.aggro.jh <- cumulative.fixation.windows.data.aggro.jh %>%
  filter(!subject_id %in% bad.subjects.validation.aggro.jh) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

@@

```
#### Re-analysis After Exclusions
Again, we excluded participants with validation accuracy under `r validation.threshold.aggro.jh`%, which eliminated `r length(bad.subjects.validation.aggro.jh)` participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))` participants.

Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).

### 2024-10-22 group-a/E1-analysis-comparison-to-JMW23.Rmd

JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND))+
  geom_line()+
  geom_point(aes(fill = obj_class), size=2, color = "black")+ 
  scale_fill_manual(name = "Object Type",values=c("white", "black"), labels = c("distractor", "target"))+
  guides(fill = guide_legend(override.aes=list(shape=21))) +
  scale_shape_manual(name = "Verb Type", values=c(22,21), labels = c("non-resticting", "restricting"))+
  theme_bw()+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type") +
  geom_vline(xintercept = mean(JMW1_info$Non.relative)) +
  theme(panel.grid=element_blank(), legend.position = "none", axis.title.x = element_blank())+
  ggtitle('James et al. (2023), Exp. 1')

>>>>

JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND))+
  geom_line()+
  geom_point(aes(fill = obj_class), size=2, color = "black")+ 
  scale_fill_manual(name = "Object Type",values=c("white", "black"), labels = c("distractor", "target"))+
  guides(fill = guide_legend(override.aes=list(shape=21))) +
  scale_shape_manual(name = "Verb Type", values=c(22,21), labels = c("non-resticting", "restricting"))+
  theme_bw()+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type") +
  geom_vline(xintercept = mean(JMW1_info$Non.relative)) +
  theme(panel.grid.minor=element_blank(), legend.position = "none", axis.title.x = element_blank())+
  ggtitle('James et al. (2023), Exp. 1')

### 2024-10-22 group-a/E1-analysis-replication.Rmd

```{r save validation percent in roi during validation}
validation.percent <- validation.accuracy.data %>%
  group_by(subject_id) %>%
  slice_tail() %>%
  select(subject_id, percent_in_roi) %>%
  unnest(percent_in_roi) %>%
  group_by(subject_id) %>%
  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
  mutate(subject_id = fct_reorder(subject_id, M))

@@

critical.trials.filtered.min <- critical.trials %>%
  filter(!subject_id %in% bad.subjects.min)

@@

<!-- This is where I should say how many people were excluded, right? -->
#### Minimal Exclusion 
The first set of analyses used minimal exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs. This resulted in the elimination of one participant. Second, we excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in an additional `r n.bad.subjects.min - length(bad.subjects.prop.samples.min)` excluded participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.min$subject_id))` participants.

@@

```{r group cumu fix by object}
cumulative.fixation.windows.grouped.data.min <- cumulative.fixation.windows.data.min %>%
  filter(!subject_id %in% bad.subjects.min) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

@@

```{r}
prop.samples.threshold.aggro <- 0.2

@@

critical.trials.filtered.aggro <- critical.trials %>%
  filter(!subject_id %in% bad.subjects.aggro)

n.bad.subjects.aggro <- length(bad.subjects.aggro)
```
#### Aggressive Exclusion
The second set of analyses used more aggressive exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.aggro*100` percent of their fixations or fewer landing in any ROIs. This resulted in the elimination of `r length(bad.subjects.prop.samples.aggro)` participants. Second, we excluded participants with validation accuracy under `r validation.threshold.aggro` percent, which eliminated an additional `r n.bad.subjects.aggro - length(bad.subjects.prop.samples.aggro)` participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants.

@@

```{r}
cumulative.fixation.windows.grouped.data.aggro <- cumulative.fixation.windows.data.aggro %>%
  filter(!subject_id %in% bad.subjects.aggro) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

@@

```
We tested the same three models under these more aggressive exclusion criteria. The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`). However, the final model, which tested the effect of verb condition on saccades to the target, yielded a statistically significant result, unlike in the previous set of analyses (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).

@@

@@

```{r E1-calib-effect, fig.cap='Calibration scores plotted against target advantage scores (cumulative proportion of fixations to the target minus cumulative proportion of fixations to competitors) at the end of the pre-noun time window.'}
#The one corr that came out: noun window, restricting condition only
ggplot(cali.analy.1, aes(x=M, y=restricting))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Target Advantage Score")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

#### Calibration
Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality varied widely, ranging from `r min(validation.percent$M) %>% round(digits = 2)`% to `r max(validation.percent$M) %>% round(digits = 2)`%.

We tested whether a participant's calibration quality was correlated with their effect size. There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions). Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`. However, when the two interaction effects were calculated as the target advantage in the restricting condition only (i.e. rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`). This is shown in Figure\ \@ref(fig:E1-calib-effect).

>>>>

```{r save validation percent in roi during validation}
validation.percent <- validation.accuracy.data %>%
  group_by(subject_id) %>%
  #slice_tail() %>%
  select(subject_id, percent_in_roi, trial_index, phase) %>%
  unnest(percent_in_roi) %>%
  group_by(subject_id, trial_index, phase) %>%
  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
  group_by(subject_id) %>%
  mutate(calib_num = row_number()) %>%
  filter(calib_num == max(calib_num)) %>%
  select(subject_id, M, calib_num) %>%
  mutate(subject_id = fct_reorder(subject_id, M))

@@

#AJ: I'm not going to do any exclusions initially to be consistent with the other Exps
# critical.trials.filtered.min <- critical.trials %>%
#   filter(!subject_id %in% bad.subjects.min)
critical.trials.filtered.min <- critical.trials #the name is a convenient lie

@@

<!-- 
#### Minimal Exclusion 
The first set of analyses used minimal exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.min*100` percent of fixations in any ROIs. This resulted in the elimination of one participant. Second, we excluded participants with validation accuracy under `r validation.threshold.min` percent, resulting in an additional `r n.bad.subjects.min - length(bad.subjects.prop.samples.min)` excluded participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.min$subject_id))` participants. 
(AJ: I'm not going to do any exclusions initially to be consistent with the other Exps) -->

@@

```{r group cumu fix by object}
cumulative.fixation.windows.grouped.data.min <- cumulative.fixation.windows.data.min %>%
  #filter(!subject_id %in% bad.subjects.min) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

@@

```{r}

prop.samples.threshold.aggro <- 0.2

@@

#AJ: we're actually just gonna use the validation criterion (for consistency)
critical.trials.filtered.aggro <- critical.trials %>%
  #filter(!subject_id %in% bad.subjects.aggro)
  filter(!subject_id %in% bad.subjects.validation.aggro)

n.bad.subjects.aggro <- length(bad.subjects.aggro)
n.bad.subjects.validation.aggro <- length(bad.subjects.validation.aggro)
```
<!--AJ: moving this discussion to the Calibration section
#### Aggressive Exclusion
The second set of analyses used more aggressive exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.aggro*100` percent of their fixations or fewer landing in any ROIs. This resulted in the elimination of `r length(bad.subjects.prop.samples.aggro)` participants. Second, we excluded participants with validation accuracy under `r validation.threshold.aggro` percent, which eliminated an additional `r n.bad.subjects.aggro - length(bad.subjects.prop.samples.aggro)` participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants. 
-->

@@

```{r}
cumulative.fixation.windows.grouped.data.aggro <- cumulative.fixation.windows.data.aggro %>%
  filter(!subject_id %in% bad.subjects.validation.aggro) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

@@

@@

<!--Calibration stuff-->

@@

```{r E1-calib-effect, fig.cap='Calibration scores plotted against the verb effect on first fixations (the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition).'}
#I picked this one because the DV is easiest to explain, and because it's the DV where the effect comes out once you drop the "bad" participants
ggplot(cali.analy.3, aes(x=M, y=diff))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Verb Effect (ms)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

### Calibration
Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality varied widely, ranging from `r min(validation.percent$M) %>% round(digits = 2)`% to `r max(validation.percent$M) %>% round(digits = 2)`%.

We tested whether a participant's calibration quality was correlated with their effect size. There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions). Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`. Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3. The figure makes clear that there is a large proportion of participants with calibration scores under 50%.

#### Re-analysis After Exclusions
We re-analyzed the data after excluding participants with calibration scores under 50% (N = `r n.bad.subjects.validation.aggro`). The following analyses thus included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants.

We tested the same three models under these more aggressive exclusion criteria. The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`). However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded a statistically significant result, unlike in the previous set of analyses with all participants included (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).

### 2024-10-22 group-c/E3-analysis-calibration.Rmd

#### Calibration Accuracy

@@

#### Correlation with Effects

@@

```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance. Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).}
# Set up facet label names for behavioral_measure variable
behav.labs <- c("Confidence", "Reaction Time")
names(behav.labs) <- c("confidence", "rt")

@@

>>>>

<!--#### Calibration Accuracy-->

@@

<!--#### Correlation with Effects-->

@@

```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance. Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).'}
# Set up facet label names for behavioral_measure variable
behav.labs <- c("Confidence", "Reaction Time")
names(behav.labs) <- c("confidence", "rt")

@@

```{r aggro exclusions}
#Identify Ps with calibration scores under 50%
validation.threshold.aggro <- 50

e3.bad.subjects.validation.aggro <- subject.calibration.score %>%
  filter(mean_percent_in_roi <= validation.threshold.aggro) %>%
  pull(subject_id) %>%
  as.character()

n.e3.bad.subjects.validation.aggro <- length(e3.bad.subjects.validation.aggro)
#26. Yikes.

#Day 1: Looking scores
t.test.data1.aggro <- t.test.data1 %>%
  filter(!subject_id %in% e3.bad.subjects.validation.aggro)

t.test.day1.aggro <- t.test(t.test.data1.aggro$M.looking.score, mu = 0.5)

#Day 2: Looking scores and Confidence
looking.confidence.correlations.subjects.filtered.aggro <- looking.confidence.correlations.subjects.filtered %>%
  filter(!subject_id %in% e3.bad.subjects.validation.aggro)

looking.confidence.correlation.t.test.aggro <- t.test(looking.confidence.correlations.subjects.filtered.aggro$r.to.z)

#Day 2: Looking scores and RT
looking.rt.correlations.subjects.filtered.aggro <- looking.rt.correlations.subjects.filtered %>%
  filter(!subject_id %in% e3.bad.subjects.validation.aggro)

looking.rt.correlation.t.test.aggro <-t.test(looking.rt.correlations.subjects.filtered.aggro$r.to.z)
```

#### Re-analysis After Exclusions
As is clear from the preceding figures, there was a large number of participants (N = `r e2.n.bad.subjects.aggro`) that had calibration scores under 50%. When we re-analyzed the subset that remained after those participants were excluded (N = `r 45-e2.n.bad.subjects.aggro`), key results were aligned with the main analyses. The looking score result was upheld such that participants looked more at the new image on Day 1 (mean: `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`) (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`)), but looking scores remained unrelated to Day 2 memory outcomes (confidence: t(`r looking.confidence.correlation.t.test.aggro$parameter`) = `r looking.confidence.correlation.t.test.aggro$statistic`, p = `r looking.confidence.correlation.t.test.aggro$p.value`; RT: t(`r  looking.rt.correlation.t.test.aggro$parameter`) = `r looking.rt.correlation.t.test.aggro$statistic`, p = `r looking.rt.correlation.t.test.aggro$p.value`).

### 2024-10-22 group-c/E3-analysis-roi.Rmd

The correlation between looking scores using the ROI method and the halves method is `r ls.cor`.

```{r E3-roi correlation of looking score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves."}
ggplot(looking.score.data %>% filter(!is.nan(looking.score.roi)), aes(x=looking.score.roi, y=looking.score.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y~x)+
  labs(x="Looking Score (ROIs)", y="Looking Score (Halves)")+
  theme_bw()+
  coord_fixed()+
  theme(panel.grid=element_blank())
```

@@

```{r E3-roi Plot of cumulative looking score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
  geom_pointrange()+
  labs(x = "Time (ms)", y = "Cumulative Looking Score (Halves)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

>>>>

The correlation between looking scores using the ROI method and the halves method is `r ls.cor` (see Figure\ \@ref(fig:E3-roi-correlation-of-looking-score).

```{r E3-roi-correlation-of-looking-score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves."}
ggplot(looking.score.data %>% filter(!is.nan(looking.score.roi)), aes(x=looking.score.roi, y=looking.score.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y~x)+
  labs(x="Looking Score (ROIs)", y="Looking Score (Halves)")+
  theme_bw()+
  coord_fixed()+
  theme(panel.grid=element_blank())
```

@@

```{r E3-roi Plot of cumulative looking score, echo=FALSE, eval = FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
#This (the fig and the DV) isn't referred to in the body of the text, so I'm cutting this for now
ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
  geom_pointrange()+
  labs(x = "Time (ms)", y = "Cumulative Looking Score (Halves)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

### 2024-10-22 group-d/E4-analysis-ROIs.Rmd

Eye-tracking on the web differs critically from in-lab eye-tracking in that the size of the display differs across participants. Thus the size of the ROIs differs across participants. The current version of the web experiment used a bounding box around each image to determine the ROI. 
This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as show in Figure \@ref(fig:E4-example-subj-looks-ROI)a. Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \@ref(fig:E4-example-subj-looks-ROI)b).

```{r E4-example-subj-looks-ROI, fig.cap = "Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants. Magenta points indicate looks that were not categorized into an ROI"}
p_box<-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+
  theme_bw()+
  theme(legend.position = "none")
p_quad<-ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+ 
  theme_bw()+
  theme(legend.position = "none")

>>>>

Eye-tracking on the web differs critically from in-lab eye-tracking in that the size of the display differs across participants. Thus the size of the ROIs differs across participants. The current version of the web experiment used a bounding box around each image to determine the ROI. 
This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as shown in Figure \@ref(fig:E4-example-subj-looks-ROI)a. Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \@ref(fig:E4-example-subj-looks-ROI)b).

```{r E4-example-subj-looks-ROI, fig.cap = "Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants. Magenta points indicate looks that were not categorized into an ROI."}
p_box<-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+
  theme_bw()+
  theme(legend.position = "none")
p_quad<-ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+ 
  theme_bw()+
  theme(legend.position = "none")
